---
title: "winloss"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{winloss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(winloss)
```

## Introduction

Inference for win-loss parameters using censored event data. The implementation focus on two prioritized events, where the first is death and the second is either a single event or a recurrent event. The methods are described in the manuscripts:

* Parner and Overgaard (2023). Estimation of win, loss probabilities and win ratio based on right-censored event data. Submitted.
* Parner and Overgaard (2023). Win-loss parameters for right-censored event data, with application to recurrent events. Submitted.

The method seem to generalize to multiple single events, Further, the events may be a combination of single events and recurrent events as long as the recurrent events are the last prioritized event.


## Example

```{r example}

## basic example code
fit <- winloss(id=hf_action$id,
               time=hf_action$time, 
               status=hf_action$status, 
               group=hf_action$group, 
               type=c(1,2), 
               at=47)
```

The fit contain a vector of the win-loss parameter *wl* ordered as: first win, first loss, second win, second loss, ect. The asumptotic variance *sigma*. For all win-loss parameters, stub say, the fit contains the standard error, *se_stub*, lower and upper 95% confidence interval, *l_stub* and *u_stub*. The coverage of the confidence interval can be changed in the win-loss function. The parameters are

* win-loss of each event type: *wl*
* total win ratio and log win ratio: *wr* and *logwr*
* total win difference: *wd*
* event specific win ratio and log win ratio: *wrk* and *logwrk*
* event specific win difference: *wrk* and *logwrk*
* total win and loss: *w* and *l*
* event specific ranking probability: *rankedk*
* total ranking probability: *ranked*

For example, display the win-ratio with 95% confidence interval:

```{r example-result}
c(fit$wr,fit$l_wr,fit$u_wr)
```


# The HF-ACTION study

The HF-ACTION data comes from the WR package. We performed some initial data cleaning:

```{r , eval=FALSE, warning=FALSE, message = FALSE}
library(WR)
library(tidyverse)
library(magrittr)

data <- hfaction_cpx9

# Rename and recode id.
data$patid <- as.numeric(substr(data$patid, 6, 12))
names(data) <- c("id","time","status","group","age60")

# Time=0 problem (id==1359)
data <- data %>%
  mutate(time=ifelse(time<0.00001, 0.01, time)) 

# time=lag(time) problem (id=662).
data <- data %>%
  group_by(id) %>%
  mutate(time=ifelse(time==lag(time, default=0),time+0.001,time))

head(data)

hf_action <- data
```
